%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{eric.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Eric}{Bridgeford}{Biomedical Engineer and Computer Scientist} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
3900 N Charles Street
Apt 516
Baltimore, MD
21218, USA
~
+1 (267) 253 8797~{\color{green} \faMobilePhone}
~
\href{mailto:ebridge2@jhu.edu}{ebridge2@jhu.edu~{\color{red} \faEnvelope}}
\href{http://ericwb.me}{ericwb.me~{\color{brown} \faGlobe}}
\href{http://github.com/ebridge2}{ebridge2~{\color{purple} \faGithub}}
\href{https://www.linkedin.com/im/ericwb95}{ericwb95~{\color{blue} \faLinkedin}}
\section{languages}
English, basic French
\section{programming}
Python, R, UNIX {\color{red} $\varheartsuit$}
Java, Matlab, SQL
C++, C
Javascript, CSS \& HTML
\section{tools}
Django, FSL, Git
Docker, EC2, S3
Android
\section{soft skills}
leadership, design, problem~solving
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2013 -- 2017}
{B.S. {\normalfont in Biomedical Engineering and Computer Science\\ minor in Applied Mathematics and Statistics}}
{Johns Hopkins University, Baltimore, MD}
{Thesis work supervised by Dr. Joshua T. Vogelstein on project entitled: \\Functional Neurodata Graphs Service: a One-Click Pipeline for the Reliable Estimation of Functional Connectomes.}

%------------------------------------------------

\entry
{2009 -- 2013}
{High School {\normalfont La Salle College High School}}
{Wyndmoor, PA}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Academic Experience}

\subsubsection{}{Positions}

\begin{entrylist}
\entry
{08/14 -- now}
{Center for Imaging Science, Johns Hopkins University}
{Baltimore, MD}
{\job{Undergraduate Researcher} under Joshua T. Vogelstein\\
Design and implementation of an open-source fMRI pipeline for robust one-click analysis. Development of extensive quality multi-modal MR quality control suite. Statistical work focusing on making inferences from fMRI connectomes.}

\entry
{05/14 -- 02/16}
{Complex Systems Group, University of Pennsylvania}
{Philadelphia, PA}
{\job{Undergraduate Researcher} under Danielle S. Bassett\\
Assisted in the development of novel network theory statistics to compare network performance. Publicly available code for assessing small world propensity in weighted, real world networks, a statistic that improves the robustness and scaling of measures of small worldness.}

\end{entrylist}

\subsection{Organizations and Volunteer Work}

\begin{entrylist}
\entry
{03/08 -- now}
{Special Olympics Male Gymnastics Coach, Hatboro YMCA}
{Hatboro, PA}
{Volunteer to mentor \& coach special needs gymnasts. Head male gymnastics coach from 03/2011 -- 05/14.}

\entry
{04/14 -- present}
{Sigma Chi Fraternity, $\Kappa\Upsilon$ Chapter}
{Baltimore, MD}
{Chapter Risk manager from 09/14 -- 05/15.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
\entry
{09/14 -- now}
{Martha A. Laverty Scholarship}
{Johns Hopkins University, Baltimore, MD}
{Grant awarded for merit achievement.}

\entry
{05/15 -- now}
{Dean's List}
{Johns Hopkins University, Baltimore, MD}
{Awarded for maintaining a GPA above a 3.5/4.0.}

\entry
{09/15}
{Everyblock API Award}
{University of Pennsylvania Pennapps, Philadelphia, PA}
{Awarded for the best application making use of the Everyblock API for app StrollSafe.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\newpage
\section{interests}

\textbf{professional:} pipeling engineering, cloud computing, data analysis, neuroscience, reproducibility, timeseries analysis.\\
\textbf{personal:} guitar, cooking, design, animals, hiking, biking, scale model warships.

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{manual}{under review pre-prints} % Print all articles from the bibliography

\printbibsection{article}{articles in peer-reviewed journals} % Print all articles from the bibliography

\printbibsection{proceedings}{posters at international conferences} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{works in progress} % Print all research reports from the bibliography

\printbibsection{misc}{talks} % Print all miscellaneous entries from the bibliography
%----------------------------------------------------------------------------------------

\end{document}
